Generalized Universe Hierarchies and First-Class Universe Levels

### 2021-02-27 arxivsub/preprint.tex
update arxiv version

\documentclass[a4paper,UKenglish,cleveref, autoref, thm-restate]{lipics-v2021}
%This is a template for producing LIPIcs articles.
%See lipics-v2021-authors-guidelines.pdf for further information.
%for A4 paper format use option "a4paper", for US-letter use option "letterpaper"
%for british hyphenation rules use option "UKenglish", for american hyphenation rules use option "USenglish"
%for section-numbered lemmas etc., use "numberwithinsect"
%for enabling cleveref support, use "cleveref"
%for enabling autoref support, use "autoref"
%for anonymousing the authors (e.g. for double-blind review), add "anonymous"
%for enabling thm-restate support, use "thm-restate"
%for enabling a two-column layout for the author/affilation part (only applicable for > 6 authors), use "authorcolumns"
%for producing a PDF according the PDF/A standard, add "pdfa"

@@

%\nolinenumbers %uncomment to disable line numbering

%\hideLIPIcs  %uncomment to remove references to LIPIcs series (logo, DOI, ...), e.g. when preparing a pre-final version to be uploaded to arXiv or another public repository

@@

\usepackage{xcolor}
\usepackage{mathpartir}
\usepackage{todonotes}
\presetkeys{todonotes}{inline}{}
\usepackage{scalerel}
\usepackage{amssymb}
\usepackage{bm}

%% \theoremstyle{definition}
%% \newtheorem{definition}{Definition}
%% \newtheorem{example}{Example}

%% \theoremstyle{theorem}
%% \newtheorem{theorem}{Theorem}
%% \newtheorem{lemma}{Lemma}

@@

We provide an Agda formalization of the contents of the paper. The formalization
is not complete, as we skip proofs involving an excessive number of equality
coercions (which are more suited to informal reasoning, using equality
reflection), and instead focus on the key points.

>>>>

\pdfoutput=1
\documentclass[a4paper,UKenglish,cleveref, autoref, thm-restate]{lipics-v2021}
%This is a template for producing LIPIcs articles.
%See lipics-v2021-authors-guidelines.pdf for further information.
%for A4 paper format use option "a4paper", for US-letter use option "letterpaper"
%for british hyphenation rules use option "UKenglish", for american hyphenation rules use option "USenglish"
%for section-numbered lemmas etc., use "numberwithinsect"
%for enabling cleveref support, use "cleveref"
%for enabling autoref support, use "autoref"
%for anonymousing the authors (e.g. for double-blind review), add "anonymous"
%for enabling thm-restate support, use "thm-restate"
%for enabling a two-column layout for the author/affilation part (only applicable for > 6 authors), use "authorcolumns"
%for producing a PDF according the PDF/A standard, add "pdfa"

@@

\nolinenumbers %uncomment to disable line numbering

\hideLIPIcs  %uncomment to remove references to LIPIcs series (logo, DOI, ...), e.g. when preparing a pre-final version to be uploaded to arXiv or another public repository

@@

\usepackage{scalerel}
\usepackage{bm}
\usepackage{hyperref}

@@

We provide an Agda formalization of the contents of the paper, at
\url{https://github.com/AndrasKovacs/universes/tree/master/agda}. The
formalization is not complete, as we skip proofs involving an excessive number
of equality coercions (which are more suited to informal reasoning, using
equality reflection), and instead focus on the key points.
